\documentclass{beamer}


\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

% \usetheme{default}
\usepackage{bookman}
\usetheme{Madrid}
\usefonttheme{serif}
\usecolortheme{beaver}
\setbeamertemplate{theorems}[numbered] 
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{frametitle}[default][center]
}

\usepackage[many]{tcolorbox}
\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{amsmath,amsfonts,amssymb,mathtools,derivative,systeme,hyperref,relsize,graphicx,ulem}
\usepackage{stmaryrd}
\usepackage{xspace}
\usepackage{pgfplots}
\usetikzlibrary{patterns,positioning,arrows.meta,shapes.geometric,calc}
\pgfplotsset{compat=1.18}
% \usefonttheme[onlymath]{serif}
\newcommand{\Mod}[1]{\ (\mathrm{mod}\ #1)}
\newcommand{\tendsto}[1]{%
    \xrightarrow{\smash{\raisebox{-2ex}{$\scriptstyle#1$}}}}

\input{macros.tex}

%\usepackage {xcolor}
\definecolor {processblue}{cmyk}{0.96,0,0,0}
%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Amortized Pairing Delegation]{Amortized Efficiency for Pairing Delegation}

\author[Adrián P. Keilty]{Adrián P. Keilty} % Your name
\institute[Chalmers]{Chalmers University of Technology} % Your institution as it will appear on the bottom of every slide, may be shorthand to save space

\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
    \frametitle{Pairings}
    \small
Let $(\Group_1,+),\,\,(\Group_2,+)$ and $(\Group_T,\cdot)$ be cyclic groups of order a $2\secpar$-bit prime $q$ where \secpar is the security parameter.
\pause
A cryptographic pairing is a map 
$$
e\colon\Group_1\times\Group_2\mapsto\Group_T\,\,\,\text{ that is }
$$ 
\pause
\vspace{-1.5em}
\begin{itemize}
    \item Non degenerate:
    If $\langle P\rangle=\Group_1$ and $\langle Q\rangle=\Group_2$ then $e\langle e(P, Q)\rangle = \Group_T$.
    \pause
    \item Bilinear:
        $e([a]P, [b]Q) = e(P, Q)^{ab} = e([b]P, [a]Q)$.  
    \pause    
    \item Computable in polynomial time. In practice, instantiated over pairing-friendly curves such as BLS12-381.
\end{itemize}
\pause
Symmetric pairings ($\Group_1=\Group_2$) \emph{break} DDH on $\mathbb{G}_1$ and
    $\mathbb{G}_2$: given $(g, g^a, g^b, g^c)$ one can test $c = ab$ via
    $e(g^a, g^b) \stackrel{?}{=} e(g, g^c)$.
\pause
    \begin{itemize}
  \item \textbf{New hardness assumption (DBDH)}: Given $(g_1, g_1^a, g_2, g_2^b, g_1^c, T)$ with
    $g_i \in \mathbb{G}_i$, hard to decide whether $T = e(g_1,g_2)^{abc}$
    or random.
\end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Pairing-based Cryptography}
    
\pause
    \small
\textbf{Joux's tripartite Diffie-Hellman}:
        Alice broadcasts $\bracket{a}P$, Bob broadcasts $\bracket{b}P$, and Charlie broadcasts $\bracket{c}P$. Each then computes the shared key
\begin{align*}
K = e(P, P)^{abc} =e([b]&P,[c]P)^a=e([a]P, [c]P)^b=e([a]P, [b]P)^c  
\\
&\uparrow\hspace{6em}\uparrow\hspace{6em}\uparrow
\\
&\text{Alice}\hspace{4.25em}\text{Bob}\hspace{4.5em}\text{Charlie}
\end{align*}
\pause
\vspace{-1em}
    \begin{itemize}
  \item \textbf{Short Signatures (BLS)}: Signatures are single $\mathbb{G}_1$
    elements; aggregation of $n$ signatures verified with a single pairing.
\pause
  \item \textbf{Identity-Based Encryption (IBE)}: User's identity string serves
    as public key (Boneh-Franklin scheme).
\pause
  \item \textbf{KZG Polynomial Commitments}: Constant-size commitments and
    opening proofs, foundational to modern zkSNARKs.
\pause
  \item \textbf{zkSNARKs (Groth16)}: Constant-size zkSNARK proofs (3 group elements) with verification reducible to 3 pairings.
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{Computational Costs}
    \input{figures/costs-histogram.tex}
\end{frame}

\begin{frame}
    \frametitle{Pairing Delegation}
    All pairing delegation protocols are 
    \begin{itemize}
        \item One-shot: 
        \item Proven unconditionally secure $\rightarrow$ This 
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{One-Shot Pairing Delegation}
    \input{figures/delegation-framework.tex}
\end{frame}

\begin{frame}
    \frametitle{Sequential Pairing Delegation}
    \input{figures/amore-flow.tex}
\end{frame}

\begin{frame}
    \frametitle{Delegation Properties}
\small
    \begin{itemize}
    \pause
	\item \textbf{Correctness}: If the \server behaves honestly, the output of the verification phase is the intended (vector of) pairing(s).	
\[	 
\myprob{\myresult=e(\AA,\BB)}{	(\pubvalue, \secvalue)\gets\onsetup(\state, {\AA},{\BB})\\
		 		\serveroutput\gets\compute(\pubvalue)\\
		 		\myresult\gets\onverify(\state,\secvalue,\serveroutput)}=1\,.
\]
\pause
	\item \textbf{Verifiability}: The \client must be able to detect with high probability when the \server returns an incorrect result.
\[	 
\myprob{\forge{\serveroutput}\gets\adversary\paren{\pubvalue}}{
		 		\forge{\serveroutput}\neq\serveroutput\\
		 		\onverify(\state,\secvalue,\serveroutput)\neq\bot}\leq\negl(\secpar)\,.
\]
\pause
	\item \textbf{Amortized Efficiency}: The \client's workload when delegating \totpairings pairings must be lower than computing them locally.
    \[
    \scalebox{0.9}{$\displaystyle
        \frac{\cost(\offsetup)+\totpairings\cdot\paren{\cost(\onsetup) + \cost(\onverify)}}{\totpairings}
        \leq \cost(e(A,B))$
    }
    \]
    \end{itemize}
\end{frame}

\begin{frame}
    \frametitle{One way to design this}
    \small
    \pause
    For \textbf{correctness} and \textbf{verifiability}: 
    \\
    \vspace{1em}
    \pause Construct a minimal verification equation in $\Group_T$ that relies on \client generated secrets for it to be satisfied. 
    \pause
    \\
    \vspace{1em}
    In particular, for public delegated inputs $(A,B)$ and generators $(P,Q,\gamma_T=e(P,Q))\in\Group_1\times\Group_2\times\Group_T$, 
    \begin{itemize}
        \setlength{\itemsep}{7.5pt}
        \pause
        \item generate secrets $(u,v,r)$, and set $\xi=\gamma_T^{-u\cdot v}=e([u]P,[-v]Q)=e(U,-V)$,
        \pause
        \item send $\pubvalue=(C,D)=([v](U+A),V-[\secexp]B)$,
        \pause
        \item request for $\serveroutput=(\rho,\gamma)=(e(A,B),e(A,D)\cdot e(C,Q))$,
        \pause
        \item and check $\left(\xi\overset{?}{=}\rho^{\secexp}\cdot\gamma\right)\wedge\left(\rho\overset{?}{\in}\Group_T\right)\,$.
    \end{itemize}
    \pause
    This guarantees unconditional security. Why?
\end{frame}

\begin{frame}
    \frametitle{One way to design this}
    \small
\begin{lemma}[Identifying forgeries]\label{lemma:sec-against-forgery}  
	Let \adversary be an algebraic adversary, $\paren{\xi,\secexp}\in\Group_T\times\Z_q^*$ the client's secret values, $\serveroutput=(\rho,\gamma)
	\in\Group_T\times\Group_T$ the output of an honest server, and \verify a verification phase consisting of the checks
	\begin{equation}
        \left(\xi\overset{?}{=}\rho^{\secexp}\cdot\gamma\right)\wedge\left(\rho\overset{?}{\in}\Group_T\right)\,.\label{eq:verif-eq}
    \end{equation}
    If $\paren{\adversary(\pubvalue)\to\forge{\serveroutput}\neq\serveroutput}\wedge\paren{\onverify(\forge{\serveroutput})\neq\bot}$ then \adversary outputs the secret \secexp.
\end{lemma}
\pause
\begin{proof}
    By the closure property of $\Group_T$,
    if $\paren{\xi=\paren{\forge{\rho}}^{\secexp}\cdot\paren{\forge{\gamma}}}\wedge\paren{\forge{\rho}\in\Group_T}$, then $\forge{\serveroutput}$ can be written as a deviation from the honest output: $\forge{\rho}=\rho\cdot\eta$ and $\forge{\gamma}=\gamma\cdot\eta^{-\secexp}$ for any public element $\eta\in\Group_T\,$. Indeed,  
    $\paren{\forge{\rho}}^{\secexp}\cdot\paren{\forge{\gamma}}
    =
    \paren{\rho\cdot\eta}^\secexp\cdot\gamma\cdot\eta^{-\secexp}=\rho^\secexp\cdot\gamma=\xi\,$.
\end{proof}
\end{frame}

\begin{frame}
    \frametitle{One way to design this}
    For \textbf{amortized efficiency}:
    \vspace{1em}
    \pause
    \begin{itemize}
        \setlength{\itemsep}{7.5pt}
        \item Sequential delegation: Reuse $\xi$ by generating in the next delegations secrets $(\secexp_i,u_i,v_i)$ such that $u_i\cdot v_i=u_j\cdot v_j\,$. The public values will still be equipped with an extra degree of freedom.  
        \pause
        \item Sample short scalars. Short $\Group_T$ exponentation is (a lot) cheaper than a full-range one.
        % \begin{align*}
        %     e(U_i,-V_i)=e(A_i,B_i)^{\secexp_i}\cdot e(A_i,V_i-[\secexp_i]B_i)\cdot e\left([v_i](U_i+A_i),\gentwo\right)
        % \end{align*}
    \end{itemize}
    \vspace{1em}
    \pause
    Wait a minute... do we still get unconditional security?
\end{frame}

\begin{frame}
    \frametitle{Meet-in-the-middle attack}
\small
\textbf{A toy example:}
\\
\vspace{1em}
Let $(\Group=\langle P\rangle,+)$ be a cyclic group of prime order $q$, 
% where $q$ is a $2\cdot\secpar$-bit integer, 
and $(\secexp_1,\secexp_2,u)$ a tuple of secret values such that 
$\secexp_1,\secexp_2\pick S\subset
\Z_q^*\,$ and $\varepsilon\pick\Z_q^*\,$. Let $\xi=[\varepsilon]P\in\Group\,$, and consider the public view 
	\begin{equation}
		\pubvalue=\begin{cases}
			\CC=[\secexp_1]\xi+\XX
			\\
			\DD=[\secexp_2]\xi+\YY
		\end{cases}\label{eq:toy-example-view}
		\,,
	\end{equation}
	where $\XX,\YY\in\Group$ are public and  $\XX\neq\CC,\YY\neq\DD$.  
    \adversary can attempt to learn the secret tuple from (\ref{eq:toy-example-view}) by picking an element 
	\begin{equation}
		\forge{\xi}\in\mathcal{I}=\left\{[t_1^{-1}](\CC-\XX)\colon t_1\in S\right\}\cap
		\left\{[t_2^{-1}](\DD-\YY)\colon t_2\in S\right\}
		\label{eq:intersection}		
	\end{equation}
	and its corresponding indexes $\forge{r}_1,\forge{r}_2\,$, 	
	which takes up to $2\cdot\size{S}$ computations.
\end{frame}

\begin{frame}
    \frametitle{Meet-in-the-middle attack}
    \input{figures/meet-in-the-middle.tex}
\end{frame}

\begin{frame}
    \frametitle{Meet-in-the-middle attack}
    \input{figures/double-DES.tex}
\end{frame}

\begin{frame}
    \frametitle{What now?}
    \small
    \pause
    If short scalars are not used, minimal efficiency is gained. If short scalars are used, no unconditional security can be proven... 
    \\
    \pause
    \vspace{1em}
    \textbf{Remark}: Once the protocol execution is finished, \adversary can no longer cheat. We could aim for everlasting security instead.
    \\
    \pause
    \vspace{1em}
    \textbf{(Unorthodox) Solution}: 
    \pause
    \begin{itemize}
        \item Add a timeout parameter to the protocol.
        \pause
        \item Bound \adversary computationally... but not in the conventional way: Assume \adversary is not more powerful than the entire Bitcoin network, i.e., \adversary is allowed to compute $2^\kappa$ scalar group multiplications per second ($\kappa$ matching the current hashrate conversion).
    \end{itemize}  
\end{frame}


\begin{frame}
    \frametitle{Adversary winning probability}
    \small
    \pause
    \textbf{Time-bound}: \adversary computes $\leq 2^\kappa$ short exponentations in $\timepar$ seconds.
    \pause
    \\
    \textbf{Best strategy}: Choose $S_1,S_2\subset\range{2^\effpar}\colon\size{S_1}+\size{S_2}\leq 2^\kappa$ and intersect sets.
    \pause
    \begin{align*}
        &\myprob{\forge{\serveroutput}\gets\adversary\paren{\pubvalue}}{
                        \forge{\serveroutput}\neq\serveroutput\\
                        \onverify(\state,\secvalue,\serveroutput)\neq\bot}
        \\[10pt]
        \pause
        \leq&\myprobNoBar{\xi\in\begin{array}{c}
            \mathrm{set}\ \{[r^{-1}](C-X):\ r\in S_1\}\\[2pt]
            \cap\\[2pt]
            \mathrm{set}\ \{[r^{-1}](D-Y):\ r\in S_2\}
            \end{array}}
            \\[10pt]
            \pause
        \leq&\myprobNoBar{\begin{array}{c}
            \mathrm{event}\ \{r_1\in S_1\}\\[2pt]
            \wedge\\[2pt]
            \mathrm{event}\ \{r_2\in S_2\}
            \end{array}}
        \leq 2^{-\statsecpar}~~~\text{ if } \effpar=\lceil\frac{\statsecpar-1}{2}+\kappa\rceil
    \end{align*}

\end{frame}

\begin{frame}
    \frametitle{Performance results}
    \input{figures/performance.tex}
\end{frame}

\begin{frame}
    \begin{center}
    
    Thank you for your attention :)
        \\
        \vspace{3em}
    Paper: eprint.iacr.org/2025/542        
    \end{center}

\end{frame}
% \begin{frame}
% 	\begin{align*}
% 		\rho^\secexp\cdot \gamma & = e(A,B)^\secexp\cdot \left(e(A,D)\cdot e(C,\gentwo)\right) 
% 		\\[0.3em]
% 		% \displaybreak[1]
% 		&=e(A,[\secexp]B)\cdot e(A,V-[\secexp]B)\cdot e\left([-\longtermsecret\cdot u^{-1}](U+A),\gentwo\right)
% 		\\[0.3em]
% 		% \displaybreak[1]
% 		& = e(A,V)\cdot e(U+A,[-\longtermsecret\cdot u^{-1}]\gentwo)
% 		\\[0.3em]
% 		% \displaybreak[1]
% 		& = e(A,V)\cdot e(U+A,-V)
% 		\\[0.3em]
% 		% \displaybreak[1]
% 		& = e(U,-V)=e(\genone,\gentwo)^{u\cdot (-\longtermsecret)\cdot u^{-1}}=\gentt^{-\longtermsecret}=\xi
% 	\end{align*}
% \end{frame}

\end{document}